Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
zlog notes
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\subsection{ZLog: A Distributed Shared Commit
Log}\label{zlog-a-distributed-shared-commit-log}

@@

\subsubsection{Consistency}\label{consistency}

\subsubsection{Striping Strategies}\label{striping-strategies}

\subsubsection{Tiering}\label{tiering}

\subsection{MDS as a sequencer}\label{mds-as-a-sequencer}

>>>>

\subsection{ZLog: A Distributed Shared-Log}

The CORFU protocol is enforced using logical storage devices.

The lua implementation of the interfaces are encoded into cluster maps
for automatic verisoning and dissemtation across the cluster.

@@

log management is supported by mds using a special directory layout
and file types.

The zlog sequencer is volatile, shared resource that requires serialized
access. in corfu the sequencer is a fast, centeralized network counter
resource.

Initially we saught to directly model the sequencer in ceph as a non-exclusive,
non-cacheable resource, forcing clients to perform round-trip access the
resource at the authoratiave MDS for the inode representing the sequencer.
However, we found that the capapbility system in Ceph is used to batch access
to cacheable resources, providing clients best-effort access to the capability
and allowing them to burst. While unexpected, this alternative mode provides
a different approach to sequencer implementation.

In Section we quantify the trade-offs of throughput and latency for the
centeralized sequencer and the batching mechanism based on capabilities.
